Some examples in extended logic counting classes

### 2016-09-07 QSO/logics.tex
9 sep

We introduce the operator $[\textbf{alfp}_{(x_1,\ldots,x_k),R}\varphi(x_1,\ldots,x_k,R)\mid\alpha(u_1,\ldots,u_k,R,p)](y_1,\ldots,y_k)$ which uses a FO-formula $\varphi$ as well as a QSO-formula $\alpha$ and takes as input a placeholder variable $p$, which is interpreted as a constant. The function $\zeta_{\varphi,\alpha}:2^{A^k} \to \nat$ is defined as $\zeta_{\varphi,\alpha}(T_{\varphi}(X)) = \sem{\alpha'}(\A,R)$ where $\alpha'$ is obtained by replacing every instance of $p$ by $\zeta_{\varphi,\alpha}(X)$.

>>>>

We introduce the operator $[\textbf{alfp}_{(x_1,\ldots,x_k),R}\varphi(x_1,\ldots,x_k,R)\mid\alpha(u_1,\ldots,u_k,R,p)](y_1,\ldots,y_k)$ which uses a FO-formula $\varphi$ as well as a QSO-formula $\alpha$ and takes as input a placeholder variable $p$, which is interpreted as a constant. We define $T^{-1}_{\varphi}(X) = Y$ as the least set $Y$ for which $T_{\varphi}(Y) = X$. The function $\zeta_{\varphi,\alpha}:2^{A^k} \to \nat$ is defined as $\zeta_{\varphi,\alpha}(X) = \sem{\alpha'}(\A,R)$ where $\alpha'$ is obtained by replacing every instance of $p$ by $\zeta_{\varphi,\alpha}(T^{-1}_{\varphi}(X))$, and $\zeta_{\varphi,\alpha}(\emptyset) = 0$. Then the operator is evaluated as $$\sem{[\textbf{alfp}_{(x_1,\ldots,x_k),R}\varphi(x_1,\ldots,x_k,R)\mid\alpha(u_1,\ldots,u_k,R,p)](y_1,\ldots,y_k)}(y_1,\ldots,y_k) = \zeta_{\varphi,\alpha}(X^*)$$, where $X^*$ is the least fixed point of $T_{\varphi}$.
